PANCHANGE_data_preprocessing

### 2020-08-12 PANCHANGE_data_preprocessing2020-07-15.Rmd
added if statements

## GLAD
```{r coping glad pcl cols}
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
```

```{r coping glad pcl summary labels}
summarytools::dfSummary(
  coping.glad.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

@@

```{r coping glad pcl cleaning}
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.pcl.raw.id)
# Inspect colnames
colnames(coping.glad.pcl.raw.id)
#Differences
dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
```

@@

## EDGI
```{r coping edgi pcl cols}
coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
dim(coping.edgi.pcl.raw)
colnames(coping.edgi.pcl.raw)
```

```{r coping edgi pcl summary labels}
summarytools::dfSummary(
  coping.edgi.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

@@

```{r coping edgi pcl cleaning}
coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to EDGI prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to EDGI prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.edgi.pcl.raw.id)
# Inspect colnames
colnames(coping.edgi.pcl.raw.id)
#Differences
dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
```

@@

## NBR
```{r coping nbr pcl cols}
coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
dim(coping.nbr.pcl.raw)
colnames(coping.nbr.pcl.raw)
```

```{r coping nbr pcl summary labels}
summarytools::dfSummary(
  coping.nbr.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

@@

```{r coping nbr pcl cleaning}
coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to NBR prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to NBR prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.nbr.pcl.raw.id)
# Inspect colnames
colnames(coping.nbr.pcl.raw.id)
#Differences
dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
```

@@

## RAMP
```{r coping ramp pcl cols}
coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
dim(coping.ramp.pcl.raw)
colnames(coping.ramp.pcl.raw)
```

```{r coping ramp pcl summary labels}
summarytools::dfSummary(
  coping.ramp.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
```

@@

```{r coping ramp pcl cleaning}
coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.ramp.pcl.raw.id)
# Inspect colnames
colnames(coping.ramp.pcl.raw.id)
#Differences
dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
```

@@

# glad COPING phq

```{r coping glad phq cols}
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
```

```{r coping glad phq summary labels}
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
```

>>>>

## GLAD
```{r coping glad pcl cols}
if(GLAD == TRUE) {
coping.glad.pcl.raw <- readRDS(file = paste0(data.raw_path,"/glad/pcl_coping_glad.rds"))
dim(coping.glad.pcl.raw)
colnames(coping.glad.pcl.raw)
}
```

```{r coping glad pcl summary labels}
if(GLAD == TRUE) {
summarytools::dfSummary(
  coping.glad.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
}
```

@@

```{r coping glad pcl cleaning}
if(GLAD == TRUE) {
coping.glad.pcl.raw.id <- coping.glad.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to GLAD prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to GLAD prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.pcl.raw.id)
# Inspect colnames
colnames(coping.glad.pcl.raw.id)
#Differences
dim(coping.glad.pcl.raw)[1]-dim(coping.glad.pcl.raw.id)[1]
}
```

@@

## EDGI
```{r coping edgi pcl cols}
if(EDGI == TRUE) {
coping.edgi.pcl.raw <- readRDS(file = paste0(data.raw_path,"/edgi/pcl_coping_edgi.rds"))
dim(coping.edgi.pcl.raw)
colnames(coping.edgi.pcl.raw)
}
```

```{r coping edgi pcl summary labels}
if(EDGI == TRUE) {
summarytools::dfSummary(
  coping.edgi.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
}
```

@@

```{r coping edgi pcl cleaning}
if(EDGI == TRUE) {
coping.edgi.pcl.raw.id <- coping.edgi.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to EDGI prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to EDGI prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.edgi.pcl.raw.id)
# Inspect colnames
colnames(coping.edgi.pcl.raw.id)
#Differences
dim(coping.edgi.pcl.raw)[1]-dim(coping.edgi.pcl.raw.id)[1]
}
```

@@

## NBR
```{r coping nbr pcl cols}
if(NBR == TRUE) {
coping.nbr.pcl.raw <- readRDS(file = paste0(data.raw_path,"/nbr/pcl_coping_nbr.rds"))
dim(coping.nbr.pcl.raw)
colnames(coping.nbr.pcl.raw)
}
```

```{r coping nbr pcl summary labels}
if(NBR == TRUE) {
summarytools::dfSummary(
  coping.nbr.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
}
```

@@

```{r coping nbr pcl cleaning}
if(NBR == TRUE) {
coping.nbr.pcl.raw.id <- coping.nbr.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to NBR prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to NBR prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.nbr.pcl.raw.id)
# Inspect colnames
colnames(coping.nbr.pcl.raw.id)
#Differences
dim(coping.nbr.pcl.raw)[1]-dim(coping.nbr.pcl.raw.id)[1]
}
```

@@

## RAMP
```{r coping ramp pcl cols}
if(RAMP == TRUE) {
coping.ramp.pcl.raw <- readRDS(file = paste0(data.raw_path,"/ramp/pcl_coping_ramp.rds"))
dim(coping.ramp.pcl.raw)
colnames(coping.ramp.pcl.raw)
}
```

```{r coping ramp pcl summary labels}
if(RAMP == TRUE) {
summarytools::dfSummary(
  coping.ramp.pcl.raw,
  graph.col = F,
  valid.col = F,
  labels.col = F
)
}
```

@@

```{r coping ramp pcl cleaning}
if(RAMP == TRUE) {
coping.ramp.pcl.raw.id <- coping.ramp.pcl.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID),
         startDate.coping = startDate) %>% # Rename startDate
  select(
    Sample, # Sample
    ID, # ID
    pcl.stressful_experience_repeated_images_base = pcl.stressful_experience_repeated_images,
    pcl.stressful_experience_upset_reminded_base = pcl.stressful_experience_upset_reminded, # differ to RAMP prepan
    pcl.stressful_situation_avoiding_activities_base = pcl.avoiding_activities_stressful_experience, # differ to RAMP prepan
    pcl.cut_people_feeling_distant_base = pcl.cut_people_feeling_distant,
    pcl.feeling_irritable_or_having_angry_outbursts_base = pcl.feeling_irritable_or_having_angry_outbursts,
    pcl.difficulty_concentrating_base = pcl.difficulty_concentrating,
    pcl.stressful_experience_repeated_images_retro = pcl.stressful_experience_repeated_images.1,
    pcl.stressful_experience_upset_reminded_retro = pcl.stressful_experience_upset_reminded.1,
    pcl.stressful_situation_avoiding_activities_retro = pcl.avoiding_activities_stressful_experience.1,
    pcl.cut_people_feeling_distant_retro = pcl.cut_people_feeling_distant.1,
    pcl.feeling_irritable_or_having_angry_outbursts_retro = pcl.feeling_irritable_or_having_angry_outbursts.1,
    pcl.difficulty_concentrating_retro = pcl.difficulty_concentrating.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.ramp.pcl.raw.id)
# Inspect colnames
colnames(coping.ramp.pcl.raw.id)
#Differences
dim(coping.ramp.pcl.raw)[1]-dim(coping.ramp.pcl.raw.id)[1]
}
```

@@

# COPING: PHQ

## GLAD
```{r coping glad phq cols}
if(GLAD == TRUE) {
coping.glad.phq.raw <- readRDS(file = paste0(data.raw_path, "/glad/phq_coping_glad.rds"))
dim(coping.glad.phq.raw)
colnames(coping.glad.phq.raw)
}
```

```{r coping glad phq summary labels}
if(GLAD == TRUE) {
summarytools::dfSummary(
  coping.glad.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```

Will need to double check these namings once we have the new cleaned data -- KT. 
```{r coping glad phq cleaning}
if(GLAD == TRUE) {
coping.glad.phq.raw.id <- coping.glad.phq.raw %>%
  drop_na(externalDataReference) %>% # Drop NAs
  distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
  separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
  mutate(ID = as.numeric(ID)
         ) %>%
  select(
    Sample, # Sample
    ID, # ID
    phq.problems_made_difficult_care,
    phq.pandemic_felt_feelings,
    phq.little_interest_or_pleasure_in_doing_things_retro = phq.little_interest_or_pleasure_in_doing_things,
    phq.feeling_down_depressed_or_hopeless_retro = phq.feeling_down_depressed_or_hopeless,
    phq.staying_asleep_sleeping_trouble_retro = phq.staying_asleep_sleeping_trouble,
    phq.feeling_tired_or_having_little_energy_retro = phq.feeling_tired_or_having_little_energy,
    phq.poor_appetite_or_overeating_retro = phq.poor_appetite_or_overeating,
    phq.feeling_bad_failure_family_retro = phq.feeling_bad_failure_family,
    phq.trouble_concentrating_reading_newspaper_retro = phq.trouble_concentrating_newspaper_reading, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_retro = phq.moving_fidgety_opposite_slowly, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_retro = phq.dead_hurting_thoughts,
    phq.little_interest_or_pleasure_in_doing_things_base = phq.little_interest_or_pleasure_in_doing_things.1,
    phq.feeling_down_depressed_or_hopeless_base = phq.feeling_down_depressed_or_hopeless.1,
    phq.staying_asleep_sleeping_trouble_base = phq.staying_asleep_sleeping_trouble.1,
    phq.feeling_tired_or_having_little_energy_base = phq.feeling_tired_or_having_little_energy.1,
    phq.poor_appetite_or_overeating_base = phq.poor_appetite_or_overeating.1,
    phq.feeling_bad_failure_family_base = phq.feeling_bad_failure_family.1,
    phq.trouble_concentrating_reading_newspaper_base = phq.trouble_concentrating_newspaper_reading.1, # differ GLAD prepandemic
    phq.moving_fidgety_noticed_opposite_base = phq.moving_fidgety_opposite_slowly.1, # differ GLAD prepandemic
    phq.dead_hurting_thoughts_base = phq.dead_hurting_thoughts.1
  ) %>%
  add_numeric(., exclude = exclude_cols) %>%
  mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
  mutate_if(is.numeric, ~na_if(., -99)) %>%
  mutate_if(is.numeric, ~na_if(., -77)) %>%
  mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
  mutate_if(is.factor, ~na_if(., "Don't know")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
  mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
  mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

# Inspect dimensions
dim(coping.glad.phq.raw.id)
# Inspect colnames
colnames(coping.glad.phq.raw.id)
#Differences
dim(coping.glad.phq.raw)[1]-dim(coping.glad.phq.raw.id)[1]
}
```

```{r coping glad gad copy}
if(GLAD == TRUE) {
  coping.phq.raw.id <- coping.glad.phq.raw.id
}
```

## EDGI
```{r coping edgi phq cols}
if(EDGI == TRUE) {
coping.edgi.phq.raw <- readRDS(file = paste0(data.raw_path, "/edgi/phq_coping_edgi.rds"))
dim(coping.edgi.phq.raw)
colnames(coping.edgi.phq.raw)
}
```

```{r coping edgi phq summary labels}
if(EDGI == TRUE) {
summarytools::dfSummary(
  coping.edgi.phq.raw,
  graph.col = F,
  valid.col = F
  #labels.col = F
)
}
```
